Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Final State with Multivariate Techniques

### 2015-12-15 paper/sec-analysis.tex
more edits
Done with corrections

We have
also explored the possible improvements
in the analysis from the use
of variable-$R$ jets~\cite{Krohn:2009zg}, finding
a similar performance as in the case of fixed-$R$ jets.
%
This is explained by the fact that
variable-$R$ jets are more suitable when
the degree of boost of the final state being reconstructed can
differ substantially~\cite{Cacciari:2008gd},
such as in heavy resonance
searches~\cite{Aad:2015fna},
where the degree of boost of the final state
is {\it a priori} unknown.

@@

Turning to the resolved category, an important aspect to account for
in the  selection
cuts is the fact that the $p_T$ distribution
of the four leading small-$R$ jets of the event can be relatively soft,
specially for the subleading jets.
%
As noted in~\cite{deLima:2014dta}, this is due to the fact
that the boost from the Higgs decay is moderate,
therefore the $p_T$ selection cuts for the small-$R$ jets cannot be too large.
%
In Fig.~\ref{fig:cutplots23}
we show the distribution in $p_T$ of the four leading
small-$R$ jets in signal and background events: we observe that both
distributions peak at $p_T \le 50$ GeV, with the signal distribution
eventually becoming dominant at large $p_T$.
%
The feasibility of triggering on four small-$R$ jets with a relatively
soft $p_T$ distribution is one of the experimental challenges for
exploiting the resolved category in this final state,
and hence the requirement that $p_T \ge 40$ GeV for
the small-$R$ jets.
%
In  Fig.~\ref{fig:cutplots23} we also show the
rapidity distribution of the the small-$R$
jets in the resolved category.
%
As expected, the production
is mostly central, more so in the case
of signal events, since backgrounds are dominated by
QCD $t$-channel exchange, therefore the
selection criteria on the jet rapidity are very efficient.

>>>>

@@

Turning to the resolved category, an important aspect to account for
in the  selection
cuts is the fact that the $p_T$ distribution
of the four leading small-$R$ jets of the event can be relatively soft,
specially for the subleading jets.
%
As noted in~\cite{deLima:2014dta}, this is due to the fact
that the boost from the Higgs decay is moderate,
therefore the $p_T$ selection cuts for the small-$R$ jets cannot be too large.
%
In Fig.~\ref{fig:cutplots23}
we show the distribution in $p_T$ of the four leading
small-$R$ jets in signal and background events: we observe that both
distributions peak at $p_T \le 50$ GeV, with the signal distribution
falling off less steeply at large $p_T$.
%
The feasibility of triggering on four small-$R$ jets with a relatively
soft $p_T$ distribution is one of the experimental challenges for
exploiting the resolved category in this final state,
and hence the requirement that $p_T \ge 40$ GeV for
the small-$R$ jets.
%
In  Fig.~\ref{fig:cutplots23} we also show the
rapidity distribution of the the small-$R$
jets in the resolved category.
%
As expected, the production
is mostly central, more so in the case
of signal events, since backgrounds are dominated by
QCD $t$-channel exchange, therefore the
selection criteria on the jet rapidity are very efficient.

### 2015-12-15 paper/sec-mcsamples.tex
Done with corrections

Background samples are generated at leading order
with {\tt SHERPA}~\cite{Gleisberg:2008ta} {\tt v2.1.1}.
%
As in the case of the signal generation,
the NNPDF 3.0 $n_f = 4$ LO set with strong coupling
$\alpha_s(m_Z^2)=0.118$ is used for all samples, and
we use as
factorisation and renormalisation scales $\mu_F=\mu_R=H_T/2$.
%
We account for the most relevant background
processes that can mimic the
 $hh\to 4b$ signal process.
%
This includes  QCD $4b$ multi-jet production, as well as
QCD $2b2j$ and $4j$ production, and top quark pair
production.
%
The latter is restricted to the fully hadronic final state,
since 
leptonic decays of top quarks can be removed by requiring
a lepton veto.
%
Single Higgs production processes such as $Z(\to b\bar{b})h(\to b\bar{b})$
and $t\bar{t}h(\to b\bar{b})$ along with electroweak backgrounds e.g $Z(\to b\bar{b})b\bar{b}$,
are much smaller than the QCD backgrounds~\cite{Wardrope:2014kya,deLima:2014dta}
and are therefore not included in the present analysis.
%

@@

As a cross-check of the {\tt SHERPA}
background cross-sections reported in Table~\ref{tab:samples}, we have produced leading-order
multi-jet samples
using {\tt MadGraph5\_aMC@NLO}, and
benchmarked them with the results for the same processes reported in
Ref.~\cite{Alwall:2014hca}.
%
For comparison with the latter numbers, 
we require that all samples include four anti-$k_T$ $R=0.5$ jets with $p_T \ge 80 $ GeV, where the leading jet must have $p_T \ge 100$ GeV, and with all jets within an acceptance of $|\eta| \le 2.5 $.
%
Using these common settings,
we find good agreement,
within the scale uncertainties, between the
{\tt MadGraph5\_aMC@NLO} and {\tt SHERPA} calculations of the multi-jet
backgrounds.

>>>>

Background samples are generated at leading order
with {\tt SHERPA}~\cite{Gleisberg:2008ta} {\tt v2.1.1}.
%
As in the case of the signal generation,
the NNPDF 3.0 $n_f = 4$ LO set with strong coupling
$\alpha_s(m_Z^2)=0.118$ is used for all samples, and
we use as
factorisation and renormalisation scales $\mu_F=\mu_R=H_T/2$.
%
We account for all relevant background
processes that can mimic the
 $hh\to 4b$ signal process.
%
This includes  QCD $4b$ multi-jet production, as well as
QCD $2b2j$ and $4j$ production, and top quark pair
production.
%
The latter is restricted to the fully hadronic final state,
since 
leptonic decays of top quarks can be removed by requiring
a lepton veto.
%
Single Higgs production processes such as $Z(\to b\bar{b})h(\to b\bar{b})$
and $t\bar{t}h(\to b\bar{b})$ along with electroweak backgrounds e.g $Z(\to b\bar{b})b\bar{b}$,
are much smaller than the QCD backgrounds~\cite{Wardrope:2014kya,deLima:2014dta}
and are therefore not included in the present analysis.
%

@@

As a cross-check of the {\tt SHERPA}
background cross-sections reported in Table~\ref{tab:samples}, we have produced leading-order
multi-jet samples
using {\tt MadGraph5\_aMC@NLO},
benchmarked with the results for the same processes reported in
Ref.~\cite{Alwall:2014hca}.
%
Using common settings, we find
agreement, within scale uncertainties,  between the
{\tt MadGraph5\_aMC@NLO} and {\tt SHERPA} calculations of
the multi-jet backgrounds.
